Universal Anonymous Signatures

### 2022-07-10 prism-backend/research/gsac/app-model-related.tex
Beginning refurbishment of the paper.
Defining Extract* and Identify* properties.

\subsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
\CUASGen with only one issuer and opener, one credential per user, and one
attribute per credential (the user secret key), implements an MPS scheme where
$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
user, and one attribute per credential, can be done as in
\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
parameterized with a value $j$, which essentially is the result of applying $F$
to the message and signer identity, and is not leaked to the opener nor any
other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
encrypted with a single-use key pair, and is an input of \yinsp.

@@

\begin{proof}
  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
  This is directly satisfied by signature unforgeability in \UAS.
  %
  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
  to produce a signature that has not been produced via a call to their \SIGN
  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
  then such adversary can be used to build an adversary winning the signature
  unforgeability game against \CUASMPS, through winning condition at line 12 --
  as \IdentifyUK does not return 1 for any known \uid. Thus, if \CUASMPS has
  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
  %
  \qed
\end{proof}

>>>>

\subsubsection{\CUASMPS construction.} %
As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
\CUASGen with only one issuer and opener, one credential per user, and one
attribute per credential (the user secret key), implements an MPS scheme where
$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
user, and one attribute per credential, can be done as in
\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
parameterized with a value $j$, which essentially is the result of applying $F$
to the message and signer identity, and is not leaked to the opener nor any
other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
encrypted with a single-use key pair, and is an input of \yinsp.

@@

\begin{proof}
  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
  This is directly satisfied by signature unforgeability in \UAS.
  %
  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
  to produce a signature that has not been produced via a call to their \SIGN
  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
  then such adversary can be used to build an adversary winning the signature
  unforgeability game against \CUASMPS, through winning condition at line 12 --
  as \IdentifySig does not return 1 for any known \uid. Thus, if \CUASMPS has
  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
  %
  \qed
\end{proof}

### 2022-07-10 prism-backend/research/gsac/app-uas-proofs.tex
Defining Extract* and Identify* properties.

First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
\IdentifyUK functions that are needed for some of the properties to be
meaningful, in \figref{fig:helper-funcs}.

@@

      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
        \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
      }

      \procedure{$\IdentifyUK(\parm,\trap,\uid,\usk)$}{%
        \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
        \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
        \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
        \pcind \pcif \usk = \usk': \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
  }
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
\end{figure}

@@

  We start from $G_0=\ExpSigAnonb$, and define game $G_1$ to be exactly the same
  as $G_0$, except that, within the $\Setup$ algorithm, we replace
  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
  $G_1$ is indistinguishable from $G_0$.

  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
  (i.e., \ExpSigAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
  % 
  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
  is, in $G_2^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.

  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
  for $b=1$, where the challenge
  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from
  $G_1^1$, simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\ceval,
  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is
  indistinguishable from $G_1^1$. Note also that $G_2^1$ and $G_2^0$ are
  indistinguishable, due to the IND-CCA property of the encryption scheme
  (so, the \ceval values in $\csig_0$ and $\csig_1$ are indistinguishable),
  in the  challenge oracle used in the anonymity game, we restrict to
  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
  the same \yinsp value (and, otherwise, \adv~is not allowed to open it).

  Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$. As
  argued, $G_1$ is indistinguishable from $\ExpSigAnonb$, thus
  $\AdvSigAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
  \AdvSigAnon is negligible.
  % 
  \qed
\end{proof}

@@

  \paragraph{(e) \usk must belong to a known user.} %
  The only remaining option for $\adv$ to win is via winning condition at line
  12, meaning that \IdentifyUK fails to find an honest or corrupt users with
  a \usk matching the one used to request the credentials used to produce the
  signature output by \adv. However, at line 12, we already know that all
  credentials are valid signatures by the issuer and that, also, all are bound
  to the same user key. If this key is not associated to any known user, this
  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
  a credential over \usk --i.e., the honest issuer did not issue any credential
  to \usk. But, as \sig must have been produced with at least one credential
  (extracted at step 7), then this credential is a forgery, breaking security
  against one-more forgery of the \SBCM scheme.
  %
  \qed
\end{proof}

@@

  First, suppose that the \Sig that \adv~outputs at line 2 exists in
  \SIG, for some \uid. Then, Given that the signature is accepted by \Verify at
  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

>>>>

First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
\IdentifySig functions that are needed for some of the properties to be
meaningful, in \figref{fig:helper-funcs}.

@@

      % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
      %   \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
      % }

      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred,\ipk)$}{%
        \pcreturn \SBCMVerify(\ipk,\cred,\usk,\attrs_{\cred}) \\
      }

      \procedure{$\IdentifySig(\parm,\trap,\usk,\scred,\Sig)$}{%
        \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
        \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
        \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
        \pcind \pcif \usk = \usk': \pcreturn 1 \\
        \pcreturn 0
      }

      % \procedure{$\IdentifySig(\parm,\trap,\uid,\usk)$}{%
      %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      %   \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      %   \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
      %   \pcind \pcif \usk = \usk': \pcreturn 1 \\
      %   \pcreturn 0
      % }

    \end{minipage}
  }
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifySig, for \CUASGen.}
\end{figure}

@@

  We start from $G_0=\ExpSigAnonb$.  %
  From $G_0$, we consider $G^0_0 = \ExpSigAnonz$. The challenge sent to the
  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
  % 
  Further, we build $G_1^0$ from $G_0^0$ by simulating the proof $\pi_0$. That
  is, in $G_1^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
  of $\NIZK^{\Sign}$, $G_1^0$ is indistinguishable from $G_0^0$.

  Similarly, we consider $G_0^1$ and $G_1^1$. That is, $G_0^1 = \ExpSigAnono$,
  where the challenge
  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, build $G_1^1$ from
  $G_0^1$, simulating $\pi_1$. That is, in $G_1^1$, $\csig_1 = (\pi_1^s,\ceval,
  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_1^1$ is
  indistinguishable from $G_0^1$. Note also that $G_1^1$ and $G_1^0$ are
  indistinguishable, due to the IND-CCA property of the encryption scheme
  (so, the \ceval values in $\csig_0$ and $\csig_1$ are indistinguishable),
  in the  challenge oracle used in the anonymity game, we restrict to
  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
  the same \yinsp value (and, otherwise, \adv~is not allowed to open it).

  Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|
  = |\Pr\lbrack G_0^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_0^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack|$, which is negligible.
  % 
  \qed
\end{proof}

@@

  \paragraph{(e) \usk must belong to a known user.} %
  The only remaining option for $\adv$ to win is via winning condition at line
  12, meaning that \IdentifySig fails to find an honest or corrupt users with
  a \usk matching the one used to request the credentials used to produce the
  signature output by \adv. However, at line 12, we already know that all
  credentials are valid signatures by the issuer and that, also, all are bound
  to the same user key. If this key is not associated to any known user, this
  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
  a credential over \usk --i.e., the honest issuer did not issue any credential
  to \usk. But, as \sig must have been produced with at least one credential
  (extracted at step 7), then this credential is a forgery, breaking security
  against one-more forgery of the \SBCM scheme.
  %
  \qed
\end{proof}

@@

  First, suppose that the \Sig that \adv~outputs at line 2 exists in
  \SIG, for some \uid. Then, Given that the signature is accepted by \Verify at
  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 7 and 8
  pass. Hence, the probability that the adversary wins at either lines 7 or 8 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.
